---
title: "W4HW"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Getting data

The raw training data has 19622 rows of observations and 158 features (predictors). Column X is unusable row number. While the testing data has 20 rows and the same 158 features. There is one column of target outcome named classe.

```{r,include=FALSE}
# load the CSV files as data.frame 
data <- read.csv("C:/Users/yiting/Desktop/pml-training.csv")
test <- read.csv("C:/Users/yiting/Desktop/pml-testing.csv")

```
#Preprocessing

Plot of relationship between features and outcome

```{r,include=T}
library(dplyr)
train <- data %>% select(roll_belt,pitch_belt,yaw_belt,
                         gyros_belt_x,gyros_belt_y,gyros_arm_z)

library(corrplot)
M <- cor(train)
corrplot(M, method="circle")
```
#Fit Model and Do 10-fold cross validation

```
library(ggplot2)
library(caret)
library(dplyr)

train <- data %>% select(roll_belt,pitch_belt,yaw_belt,
                         gyros_belt_x,gyros_belt_y,gyros_arm_z,classe)

fitControl <- trainControl(
  method = "repeatedcv",
  number = 10,
  repeats = 3,
  classProbs = TRUE
)

set.seed(1)
nbfit <- train(classe~., data = train,
                method = "nb",   
                trControl = fitControl,
                na.action = na.pass
)
```

#Prediction and Do confusionMatrix

```
test <- test %>% select(roll_belt,pitch_belt,yaw_belt,
                         gyros_belt_x,gyros_belt_y,gyros_arm_z)

pred <- predict(nbfit,test,type="raw")
confusionMatrix(pred,test$classe)

```

